Comparison of Catalogs

### 2024-07-30 compare/compare.qmd
K Lum and Mag

```{python}
#| echo: false
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support, hist
#quantity_support()
from astropy.stats import sigma_clip
from astropy.modeling import models, fitting
from scipy.stats import pearsonr
import seaborn as sns
import pandas as pd
import glob
import os
plt.style.use('ggplot')
pd.set_option('display.float_format', lambda x: '%.f' % x)

@@

    Returns:
    tuple: A tuple containing the following elements:
        - slope (float): The slope of the fitted linear model.
        - intercept (float): The intercept of the fitted linear model.
        - r2 (float): The R-squared value, indicating the proportion of variance explained by the linear model.
        - corr (float): The Pearson correlation coefficient, measuring the linear correlation between x and y.
    """
    try:
        x_data = np.ma.array(x.value, mask=np.isnan(x.value)&x.mask)
        y_data = np.ma.array(y.value, mask=np.isnan(y.value))
        # initialize a linear fitter
        fit = fitting.LinearLSQFitter()

@@

\[?\] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference. \## Heatmap

@@

```{python}
dt["INCL"].mask = np.isnan(dt["INCL"])
```
```{python}
#| echo: false

@@

```{python}
scatter_plot(dt["log_a26"], dt["log_R1"], sigma = True)
```

:::
## Luminosities

@@

```{python}
#| echo: false
scatter_plot(dt["logKLum"], dt["logL_K"], sigma = True)
```

@@

```{python}
scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
```

@@

```{python}
dt["diff_K_mag"] = relative_diff(dt["Kmag"], dt["K"])
dt["diff_K_mag"].info("stats")
```

```{python}
sns.histplot(dt["diff_K_mag"], kde = True)
plt.title("Percentage change Distribution [%]")
plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
plt.show()
```
:::

>>>>

```{python}
#| echo: false
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support, hist
#quantity_support()
from astropy.stats import sigma_clip, SigmaClip
from astropy.modeling import models, fitting
from scipy.stats import pearsonr
import seaborn as sns
import pandas as pd
import glob
import os
plt.style.use('ggplot')
pd.set_option('display.float_format', lambda x: '%.f' % x)

@@

    Returns:
    tuple: A tuple containing the following elements:
        - slope (float): The slope of the fitted linear model.
        - intercept (float): The intercept of the fitted linear model.
        - r2 (float): The R-squared value, indicating the proportion of variance explained by the linear model.
        - corr (float): The Pearson correlation coefficient, measuring the linear correlation between x and y.
    """
    try:
        x_data = np.ma.array(x.value, mask=np.isnan(x.value))
        y_data = np.ma.array(y.value, mask=np.isnan(y.value))
        # initialize a linear fitter
        fit = fitting.LinearLSQFitter()

@@

\[?\] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference.

## Heatmap

@@

```{python}
dt["INCL"].mask = np.isnan(dt["INCL"])
```

```{python}
#| echo: false

@@

```{python}
scatter_plot(dt["log_a26"], dt["log_R1"], sigma = True)
```
:::

## Luminosities

@@

```{python}
#| echo: false
dt["diff_L_K"] = relative_diff(hec = dt["logL_K"].value, lcv = dt["logKLum"])
temp = dt[["logKLum", "logL_K", "diff_L_K"]].to_pandas()
sns.histplot(temp["diff_L_K"], kde = True)
plt.xlabel("Percentage change [%]")
plt.title("K-band Luminosities")
plt.show()
```

```{python}
temp.rename(columns = {"logKLum":"log(L_K)_{LCV}$", "logL_K":"log(L_K)_{HEC}", "diff_L_K":"Percentage Change [%]"}, inplace=True)
```

```{python}
temp.describe()
```

@@

```{python}
scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma=True)
```

@@

```{python}
dt["diff_K_mag"] = relative_diff(dt["Kmag"], dt["K"])

temp = dt[["diff_K_mag"]].to_pandas()
c = temp["diff_K_mag"]
up_clip = c.mean() + 3*c.std()
low_clip = c.mean() - 3*c.std()
temp["Percentage Change, after 3 sigma clip [%]"] = temp["diff_K_mag"].clip(low_clip, up_clip)
temp.rename(columns={"diff_K_mag":"Percentage Change [%]"}, inplace=True)
temp.describe()
```

```{python}
sns.histplot(temp, kde = True)
plt.title("Percentage change Distribution [%]")
plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
plt.show()
```
:::
